Name matching through deep learning

### 2018-11-30 old/paper2018/evaluation.tex
fixing more numbers to be consistent with tables

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The numbers for the adapted loss function were 81\% for people and 74\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies the only significant difference was that angular was worse.

 Precision is a little trickier to define, but one way is to measure it is to examine how many true matches we get in the neighborhood of each anchor before seeing a single mistake, i.e. a match that should not be there.  That metric gives a picture of how many names would be correctly found, on average, by a join.  Adapted loss is at 63\% by this metric for people and 66\% for companies, so about two thirds of recalled names would be found before finding a single error.  Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.  For that, the very best performance we get is 84\% for people and 75\% for companies.

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.  For companies, it is from 16\% to 74\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.  Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.  In both these cases, demonstrable training occurred.

>>>>

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The best numbers across the models were 82\% for people and 76\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies, triplet loss seemed the best, which suggests that the properties of the dataset combine with loss functions to influence performance.

 Precision is a little trickier to define, but one way is to measure it is to examine how many true matches we get in the neighborhood of each anchor before seeing a single mistake, i.e. a match that should not be there.  That metric gives a picture of how many names would be correctly found, on average, by a join.  Adapted loss is at 61\% by this metric for people and triplet loss is at 67\% for companies, so about two thirds of recalled names would be found before finding a single error.  Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.  For that, the very best performance we get is 82\% for people and 76\% for companies.

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.  For companies, it is from 16\% to 76\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 61\% for people and 16\% to 67\% for companies.  Precision@1 improves from 10\% to 82\% for people and from 26\% to 76\% for companies.  In both these cases, demonstrable training occurred.
